\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1.2cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[dvipsnames]{xcolor}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{microtype}

\definecolor{ink}{RGB}{10,10,10}
\definecolor{accent}{RGB}{181,121,0}
\definecolor{muted}{RGB}{82,82,82}
\hypersetup{colorlinks=true,urlcolor=ink}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\tabcolsep}{0pt}
\setlist[itemize]{leftmargin=1.15em,itemsep=1pt,topsep=2pt,parsep=0pt}
\titleformat{\section}{\large\bfseries}{}{0pt}{}[\vspace{1pt}{\color{accent}\rule{\linewidth}{1.2pt}}]
\titlespacing*{\section}{0pt}{8pt}{5pt}
\newcommand{\job}[4]{%
  \begin{tabularx}{\linewidth}{@{}Xr@{}}
    {\bfseries #1} \quad {\color{accent}\textbf{#2}} & {\color{muted}#3} \\
  \end{tabularx}
  #4
}

\begin{document}
\color{ink}

\begin{tabularx}{\linewidth}{@{}Xr@{}}
{\fontsize{25}{27}\selectfont\bfseries Aníbal Fermandois} &
\begin{tabular}{r@{}}
\href{mailto:anibal.fermandois@gmail.com}{anibal.fermandois@gmail.com}\\
+569-6617-0056\\
\href{https://www.anibalfermandois.com/}{www.anibalfermandois.com}
\end{tabular}\\
\end{tabularx}
{\large Full-Stack Developer, AI Infrastructure Builder, Technical Lead in Training}\\
\vspace{3pt}
\href{https://www.linkedin.com/in/anibal-fermandois-224ab4262/}{linkedin.com/anibal-fermandois}

\section{What I Bring}
I build useful systems from undefined requirements: clarify the decision, find the data, test the model, ship the product surface, and keep the infrastructure understandable. My strongest work sits between software engineering, analytics, and technical leadership.

\section{Professional Work}
\job{Falabella}{Planning and Development Engineer}{May 2026 -- Present}{
\begin{itemize}
  \item Turn messy historical BigQuery data into metrics and assumptions that support store allocation and replenishment decisions.
  \item Use Python, pandas, and polars to explore nonlinear behavior, patch inconsistent data, and compare model behavior under different filters.
  \item Communicate analytical findings as concrete recommendations for future operating policy.
\end{itemize}}

\job{Buda.com}{Automation and AI Intern}{Aug 2025 -- Dec 2025}{
\begin{itemize}
  \item Shipped an internal AI chatbot with complex API integrations, advanced RAG, Contextual Chunking, HyDE, and context engineering.
  \item Improved retrieval quality with Contextual Embedding and MultiVector Indexing, reaching above 95\% answer accuracy.
  \item Built n8n automation pipelines for critical business processes with reliability and maintenance in mind.
\end{itemize}}

\job{Nikola Chile}{Full-Stack Developer}{Mar 2025 -- Aug 2025}{
\begin{itemize}
  \item Owned the Next.js and Django architecture behind \href{https://www.nikola.cl}{nikola.cl}, from frontend implementation to backend and deployment decisions.
  \item Led modernization from legacy systems to scalable web infrastructure, including code-quality automation and monitoring tools.
  \item Received recognition for leadership and delivery on the current company website.
\end{itemize}}

\job{Preuniversitario PreuIng UC}{Teacher}{1 year}{}
\job{Proyecto Going UC}{Teacher}{1 year}{}
\job{Debates Constitucionales}{Head Teaching Assistant}{2 years}{}

\section{Projects}
\begin{itemize}
  \item \textbf{\href{https://beascorner.onrender.com/}{Bea's Corner}} -- Marketplace data product for makeup availability and prices across Chilean retailers.
  \item \textbf{\href{https://bcibeneficios.onrender.com/}{BCI Beneficios}} -- Faster BCI+ discounts experience with filters, categories, minimums, and caps.
  \item \textbf{\href{https://micarritochile.vercel.app/}{Mi Carrito}} -- E-commerce price comparison using automated supermarket scrapers.
\end{itemize}

\section{Education \& Stack}
\begin{tabularx}{\linewidth}{@{}X@{\hspace{0.6cm}}X@{}}
\textbf{Pontificia Universidad Católica de Chile} & \textbf{Languages:} Python, JavaScript, TypeScript, Mojo, C, SQL \\
Industrial Civil Engineering, Computing Diploma, 2020 -- Present & \textbf{Tools:} Django, Astro, Next.js, React, n8n, Postgres, MongoDB, AWS, Vercel, Render \\
Frontend Development Certificate, Launchpad & \textbf{Human languages:} English C1 TOEFL, French B1 ICP Université, Spanish native \\
\end{tabularx}

\end{document}
