\documentclass[10pt,letterpaper]{article}
\usepackage[margin=1.15cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage[dvipsnames]{xcolor}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{microtype}

\definecolor{ink}{RGB}{18,24,33}
\definecolor{accent}{RGB}{0,86,122}
\definecolor{muted}{RGB}{91,103,112}
\hypersetup{colorlinks=true,urlcolor=accent}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\tabcolsep}{0pt}
\setlist[itemize]{leftmargin=1.2em,itemsep=1pt,topsep=2pt,parsep=0pt}
\titleformat{\section}{\bfseries\large\color{ink}}{}{0pt}{\MakeUppercase}[\vspace{-2pt}{\color{accent}\rule{\linewidth}{0.7pt}}]
\titlespacing*{\section}{0pt}{8pt}{5pt}
\newcommand{\role}[4]{%
  \begin{tabularx}{\linewidth}{@{}Xr@{}}
    \textbf{#1} \hspace{3pt} {\color{accent}#2} & {\color{muted}#3} \\
  \end{tabularx}
  #4
}

\begin{document}
\color{ink}

{\fontsize{26}{28}\selectfont\bfseries Aníbal Fermandois}\\
{\large AI Infrastructure \& Full-Stack Software Engineer}\\
\vspace{3pt}
\href{mailto:anibal.fermandois@gmail.com}{anibal.fermandois@gmail.com} \quad
+569-6617-0056 \quad
\href{https://www.linkedin.com/in/anibal-fermandois-224ab4262/}{linkedin.com/anibal-fermandois} \quad
\href{https://www.anibalfermandois.com/}{www.anibalfermandois.com}

\section{Positioning}
Software engineer and Industrial Civil Engineering student focused on AI infrastructure, automation, analytics, and full-stack product delivery. I work well where the problem is not fully specified yet: defining metrics, testing assumptions, building the system, and turning results into operational decisions.

\section{Experience}
\role{Falabella}{Planning and Development Engineer}{May 2026 -- Present}{
\begin{itemize}
  \item Explore historical BigQuery data with Python, pandas, and polars to define metrics, filters, and assumptions for store allocation and replenishment policy.
  \item Test models, inspect nonlinear behavior, patch inconsistent data, and convert analysis into concrete recommendations for future supply decisions.
\end{itemize}}

\role{Buda.com}{Automation and AI Intern}{Aug 2025 -- Dec 2025}{
\begin{itemize}
  \item Led research and production deployment of an enterprise AI chatbot integrating complex APIs, Contextual Chunking, HyDE, and context engineering, reaching above 95\% answer accuracy.
  \item Built high-precision retrieval with Contextual Embedding and MultiVector Indexing, improving relevance across internal knowledge sources.
  \item Architected robust n8n automation pipelines for critical company workflows, balancing reliability, maintainability, and speed.
\end{itemize}}

\role{Nikola Chile}{Full-Stack Developer}{Mar 2025 -- Aug 2025}{
\begin{itemize}
  \item Designed and shipped the high-performance Next.js and Django architecture for \href{https://www.nikola.cl}{nikola.cl}, owning frontend, backend, deployment, and quality decisions.
  \item Led migration from legacy systems to scalable web architecture with automated code-quality pipelines and infrastructure visibility.
  \item Recognized for leadership and delivery on the current company website.
\end{itemize}}

\role{Preuniversitario PreuIng UC}{Teacher}{1 year}{}
\role{Proyecto Going UC}{Teacher}{1 year}{}
\role{Debates Constitucionales}{Head Teaching Assistant}{2 years}{}

\section{Selected Projects}
\begin{itemize}
  \item \textbf{\href{https://beascorner.onrender.com/}{Bea's Corner}} -- Astro marketplace scraper that centralizes makeup pricing and availability across Chilean retailers.
  \item \textbf{\href{https://bcibeneficios.onrender.com/}{BCI Beneficios}} -- Faster, more usable BCI+ discounts experience with filters, categories, minimums, and caps.
  \item \textbf{\href{https://micarritochile.vercel.app/}{Mi Carrito}} -- Price comparison platform using automated scrapers for Chilean supermarkets.
\end{itemize}

\section{Education}
\begin{tabularx}{\linewidth}{@{}Xr@{}}
\textbf{Pontificia Universidad Católica de Chile} -- Industrial Civil Engineering, Computing Diploma & 2020 -- Present \\
\end{tabularx}
Frontend Development Certificate, Launchpad.

\section{Stack}
\textbf{Languages:} Python, JavaScript, TypeScript, Mojo, C, SQL \\
\textbf{Tools:} Django, Astro, Next.js, React, n8n, Postgres, MongoDB, AWS, Vercel, Render \\
\textbf{Human languages:} English C1 TOEFL, French B1 ICP Université, Spanish native

\end{document}
